### 2021-06-23 src/paper.tex
Remove suggestion by Annika.
Add some comments. Add all tex files as pytask dependencies. Fix typo in README on how to propose replacements.
Commenting out, new pdf, and updated readme.
Put comments back in. Minor corrections in the README. Add references to our code in the first paragraph of the appendix.

\input{paper/preamble}

@@

>>>>

% To ``accept'' all changes in the document:
% \PassOptionsToPackage{final}{changes}

\documentclass[a4paper, 10pt]{article}
% fleqn: flush-left aligned equations

\newcommand{\papertitle}{
The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs
}

\input{templates/Preamble_Fundamental_packages}
\hypersetup{
    pdftitle={\papertitle},
    pdfauthor={Janoś Gabler, Tobias Raabe, Klara Röhrl, Hans-Martin von Gaudecker}
}

% packages ======================================================================

\input{templates/Preamble_Page_layout_general}
\input{templates/Preamble_Page_layout_paper}
\subimport{templates/}{Preamble_Fonts_Charter_FiraSans}
\input{templates/Preamble_Sansserif_math}
\input{templates/Preamble_BibLaTeX_AER}
%\input{templates/Preamble_BibLaTeX_APA}
\input{templates/Preamble_Commenting_and_highlighting}
\input{templates/Preamble_Miscellaneous}

% Add global hyphenation rules to avoid unwelcome linebreaks:
% \hyphenation{Bu-shong Della-Vigna}

\bibliography{references.bib}

% \usepackage[newfloat, outputdir=../bld, cache=false]{minted}

% Define environments to comment on the sidebar of the PDF.
\definechangesauthor[name={Tobias}, color=alizarin]{T}
\definechangesauthor[name={Janos}, color=internationalorange]{J}
\definechangesauthor[name={Klara}, color=dartmouthgreen]{K}
\definechangesauthor[name={HM}, color=blue]{HM}
% Use \replaced[id=T]{<to-be-replaced>}{<new>} or the same with \deleted to propose
% changes.

@@

    This paper aims to be completely reproducible. The code for the general model can be
    found at
    \href{https://github.com/covid-19-impact-lab/sid/}{https://github.com/covid-19-impact-lab/sid/}
    and its documentation at
    \href{https://sid-dev.readthedocs.io/en/latest/}{https://sid-dev.readthedocs.io/en/latest/}.
    The code for the application to Germany can be found at
    \href{https://github.com/covid-19-impact-lab/sid-germany/}{https://github.com/covid-19-impact-lab/sid-germany/}
    with a very rudimentary documentation at
    \href{https://sid-germany.readthedocs.io/en/latest/}{https://sid-germany.readthedocs.io/en/latest/}.

### 2021-06-23 src/paper/report.tex
Put comments back in. Minor corrections in the README. Add references to our code in the first paragraph of the appendix.

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the
three channels for rapid tests. Tests at schools have the smallest effect, which is
largely explained by schools not operating at full capacity during our period of study
and the relatively small number of students.\footnote{18\% of our population are in the
education sector (pupils, teachers, etc.); 46\% are workers outside the education sector}
Almost 40\% come from tests at the workplace. Despite the fact that rapid tests for
private reasons are phased in only late, they make up for more than half of the total
effect. The reason lies in the fact that a substantial share of these tests is driven by
an elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or
following up on a positive test of a household member. The latter is essentially a form
of contact tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020,FetzerGraeber2021}.

>>>>

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the three
channels for rapid tests. Tests at schools have the smallest effect, which is largely
explained by schools not operating at full capacity during our period of study and the
relatively small number of students.\footnote{18\% of our population are in the education
sector (pupils, teachers, etc.); 46\% are workers outside the education sector.} Almost
40\% come from tests at the workplace. Despite the fact that rapid tests for private
reasons are phased in only late, they make up for more than half of the total effect. The
reason lies in the fact that a substantial share of these tests is driven by an elevated
probability to carry the virus, i.e., showing symptoms of CoViD-19 or following up on a
positive test of a household member. The latter is essentially a form of contact tracing,
which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020,FetzerGraeber2021}.
